### 2017-03-26 Thesis/latex/outline.tex
New run

\noindent Henrik Kalisch, Daulet Moldabayev, Olivier Verdier: \textit{A numerical study of nonlinear dispersive wave models with SpecTraVVave}, \textcolor{red}{specify status of the paper.}

>>>>

\noindent Kalisch, H., Moldabayev, D., Verdier, O.: \textit{A numerical study of nonlinear dispersive wave models with SpecTraVVave}, Electronic Journal of Differential Equations~ \textbf{2017}, No. 62, pp. 1--23 (2017), http://ejde.math.txstate.edu or http://ejde.math.unt.edu.

### 2017-03-26 Thesis/latex/preface.tex
New run

The advisory committee has consisted of Henrik Kalisch (University of Bergen, Bergen, Norway),  Dmitry Pelinovsky (McMaster University, Hamilton, Ontario, Canada) and Angel Dur\'an (Universidad de Valladolid, Valladolid, Spain).

>>>>

The advisory committee has consisted of Henrik Kalisch and Guttorm Alendal (University of Bergen, Bergen, Norway),  Dmitry Pelinovsky (McMaster University, Hamilton, Ontario, Canada) and Angel Dur\'an (Universidad de Valladolid, Valladolid, Spain).
